Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic data sets with *mice*

### 2021-10-04 mice_synthesizing/paper.Rmd

Similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011]. Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is overimputed with missing values. Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue. The adjusted variance estimate that follows from using multiple synthetic data sets only suffers from the fact that a finite number of $m$ synthetic data sets are used to resemble the observed data. Hence, the according variance estimate for synthetic data as developed by @reiter_partially_inference_2003 yields
$$
T = \bar{u}_m + \frac{b_m}{m},
$$
with between variance

$$
b_m = \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\
$$
and sampling variance
$$
\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
$$
with $u^{(l)}$ reflecting the variance estimate in the $l$th synthetic data set.

# Simulation results
```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}
plan(multisession) # increase speed through futures

>>>>

Similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011]. Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is overimputed with missing values. Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue. The adjusted variance estimate that follows from using multiple synthetic data sets only suffers from the fact that a finite number of $m$ synthetic data sets are used to resemble the observed data. Hence, the according variance estimate for synthetic data as developed by @reiter_partially_inference_2003 yields
$$
T = \bar{u}_m + \frac{b_m}{m},
$$

with between-imputation variance

$$
b_m = \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\
$$
and sampling variance

$$
\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
$$
with $u^{(l)}$ reflecting the variance estimate in the $l$th synthetic data set.

# Simulation results

```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}
plan(multisession) # increase speed through futures
